Evaluating Regularization

### 2019-03-28 Scripts/evaluating_feature_reduction.Rmd
editted script for evaluating elastic net

### G12878

@@

@@

@@

```{r}
heatmap.2(enetcoefsmat[,9:12],
          #cellnote = cormat,  # same data set for cell labels
          #main = "Correlation", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins =c(5,5),     # widens margins around plot
          col=my_palette,       # use on color palette defined earlier
          na.color = "gray",
          #breaks=col_breaks,    # enable color transition at specified limits
          key=FALSE,
          dendrogram="row",     # only draw a row dendrogram
          cexRow=0.5,
          cexCol=0.75,
          #labRow = FALSE,
          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
          #lhei=c(.5,6,0),
          sepwidth=c(0.001,0.001),
          sepcolor="black",
          colsep=1:4,
          rowsep=1:nrow(enetcoefsmat),
          keysize = 1) 
```

@@

>>>>

@@

```{r}
heatmap.2(enetcoefsmat[,1:4],
          #cellnote = cormat,  # same data set for cell labels
          #main = "Correlation", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins =c(5,5),     # widens margins around plot
          col=my_palette,       # use on color palette defined earlier
          na.color = "gray",
          #breaks=col_breaks,    # enable color transition at specified limits
          key=FALSE,
          #key.title = "Elastic-Net\nCoefficient",
          #keysize = 1.5,
          dendrogram="none",     # only draw a row dendrogram,
          Rowv = FALSE,
          Colv = FALSE,
          cexRow=0.5,
          cexCol=0.75,
          #labRow = FALSE,
          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
          #lhei=c(.5,6,0),
          sepwidth=c(0.001,0.001),
          sepcolor="black",
          colsep=1:4,
          rowsep=0:nrow(enetcoefsmat)) 
```

@@

```{r}
heatmap.2(enetcoefsmat[,5:8],
          #cellnote = cormat,  # same data set for cell labels
          #main = "Correlation", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins =c(5,5),     # widens margins around plot
          col=my_palette,       # use on color palette defined earlier
          na.color = "gray",
          #breaks=col_breaks,    # enable color transition at specified limits
          key=FALSE,
          #key.title = "Elastic-Net\nCoefficient",
          #keysize = 1.5,
          dendrogram="row",     # only draw a row dendrogram,
          #Rowv = FALSE,
          #Colv = FALSE,
          cexRow=0.5,
          cexCol=0.75,
          #labRow = FALSE,
          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
          #lhei=c(.5,6,0),
          sepwidth=c(0.001,0.001),
          sepcolor="black",
          colsep=1:4,
          rowsep=1:nrow(enetcoefsmat)) 
```

@@

```{r}
heatmap.2(enetcoefsmat[,9:12],
          #cellnote = cormat,  # same data set for cell labels
          #main = "Correlation", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins =c(5,5),     # widens margins around plot
          col=my_palette,       # use on color palette defined earlier
          na.color = "gray",
          #breaks=col_breaks,    # enable color transition at specified limits
          key=FALSE,
          #key.title = "Elastic-Net\nCoefficient",
          #keysize = 1.5,
          dendrogram="row",     # only draw a row dendrogram,
          #Rowv = FALSE,
          #Colv = FALSE,
          cexRow=0.5,
          cexCol=0.75,
          #labRow = FALSE,
          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
          #lhei=c(.5,6,0),
          sepwidth=c(0.001,0.001),
          sepcolor="black",
          colsep=1:4,
          rowsep=1:nrow(enetcoefsmat)) 
```

#####All

```{r}
heatmap.2(enetcoefsmat,
          #cellnote = cormat,  # same data set for cell labels
          #main = "Correlation", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins =c(5,5),     # widens margins around plot
          col=my_palette,       # use on color palette defined earlier
          na.color = "gray",
          #breaks=col_breaks,    # enable color transition at specified limits
          key=FALSE,
          #key.title = "Elastic-Net\nCoefficient",
          #keysize = 1.5,
          dendrogram="row",     # only draw a row dendrogram,
          Rowv = TRUE,
          Colv = FALSE,
          cexRow=0.5,
          cexCol=0.75,
          #labRow = FALSE,
          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
          #lhei=c(.5,6,0),
          sepwidth=c(0.001,0.001),
          sepcolor="black",
          colsep=0:12,
          rowsep=0:nrow(enetcoefsmat)) 
```

@@

#####All

```{r}
heatmap.2(enetcoefsmat,
          #cellnote = cormat,  # same data set for cell labels
          #main = "Correlation", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins =c(5,5),     # widens margins around plot
          col=my_palette,       # use on color palette defined earlier
          na.color = "gray",
          #breaks=col_breaks,    # enable color transition at specified limits
          key=FALSE,
          #key.title = "Elastic-Net\nCoefficient",
          #keysize = 1.5,
          dendrogram="row",     # only draw a row dendrogram,
          Rowv = TRUE,
          Colv = FALSE,
          cexRow=0.5,
          cexCol=0.75,
          #labRow = FALSE,
          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
          #lhei=c(.5,6,0),
          sepwidth=c(0.001,0.001),
          sepcolor="black",
          colsep=0:12,
          rowsep=0:nrow(enetcoefsmat)) 
```

#### 50kb

#None
##OC
enetcoefs_none_oc_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OC/ENET/enetModel.rds")
enetcoefs_none_oc_50kb_gm12878 <- coef(enetcoefs_none_oc_50kb_gm12878$finalModel, s=enetcoefs_none_oc_50kb_gm12878$bestTune$lambda)
##OP
enetcoefs_none_op_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OP/ENET/enetModel.rds")
enetcoefs_none_op_50kb_gm12878 <- coef(enetcoefs_none_op_50kb_gm12878$finalModel, s=enetcoefs_none_op_50kb_gm12878$bestTune$lambda)
##Distance
enetcoefs_none_dist_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/ENET/enetModel.rds")
enetcoefs_none_dist_50kb_gm12878 <- coef(enetcoefs_none_dist_50kb_gm12878$finalModel, s=enetcoefs_none_dist_50kb_gm12878$bestTune$lambda)

#RUS
##OC
enetcoefs_RUS_oc_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OC/ENET/enetModel.rds")
enetcoefs_RUS_oc_50kb_gm12878 <- coef(enetcoefs_RUS_oc_50kb_gm12878$finalModel, s=enetcoefs_RUS_oc_50kb_gm12878$bestTune$lambda)
##OP
enetcoefs_RUS_op_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OP/ENET/enetModel.rds")
enetcoefs_RUS_op_50kb_gm12878 <- coef(enetcoefs_RUS_op_50kb_gm12878$finalModel, s=enetcoefs_RUS_op_50kb_gm12878$bestTune$lambda)
##Distance
enetcoefs_RUS_dist_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/ENET/enetModel.rds")
enetcoefs_RUS_dist_50kb_gm12878 <- coef(enetcoefs_RUS_dist_50kb_gm12878$finalModel, s=enetcoefs_RUS_dist_50kb_gm12878$bestTune$lambda)

#ROS
##OC
enetcoefs_ROS_oc_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OC/ENET/enetModel.rds")
enetcoefs_ROS_oc_50kb_gm12878 <- coef(enetcoefs_ROS_oc_50kb_gm12878$finalModel, s=enetcoefs_ROS_oc_50kb_gm12878$bestTune$lambda)
##OP
enetcoefs_ROS_op_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OP/ENET/enetModel.rds")
enetcoefs_ROS_op_50kb_gm12878 <- coef(enetcoefs_ROS_op_50kb_gm12878$finalModel, s=enetcoefs_ROS_op_50kb_gm12878$bestTune$lambda)
##Distance
enetcoefs_ROS_dist_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/ENET/enetModel.rds")
enetcoefs_ROS_dist_50kb_gm12878 <- coef(enetcoefs_ROS_dist_50kb_gm12878$finalModel, s=enetcoefs_ROS_dist_50kb_gm12878$bestTune$lambda)

#SMOTE
##OC
enetcoefs_SMOTE_oc_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OC/ENET/enetModel.rds")
enetcoefs_SMOTE_oc_50kb_gm12878 <- coef(enetcoefs_SMOTE_oc_50kb_gm12878$finalModel, s=enetcoefs_SMOTE_oc_50kb_gm12878$bestTune$lambda)
##OP
enetcoefs_SMOTE_op_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OP/ENET/enetModel.rds")
enetcoefs_SMOTE_op_50kb_gm12878 <- coef(enetcoefs_SMOTE_op_50kb_gm12878$finalModel, s=enetcoefs_SMOTE_op_50kb_gm12878$bestTune$lambda)
##Distance
enetcoefs_SMOTE_dist_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/ENET/enetModel.rds")
enetcoefs_SMOTE_dist_50kb_gm12878 <- coef(enetcoefs_SMOTE_dist_50kb_gm12878$finalModel, s=enetcoefs_SMOTE_dist_50kb_gm12878$bestTune$lambda)

enetcoefsmat <- cbind(enetcoefs_none_oc_50kb_gm12878[-1,1], 
                      enetcoefs_ROS_oc_50kb_gm12878[-1,1],
                      enetcoefs_RUS_oc_50kb_gm12878[-1,1], 
                      enetcoefs_SMOTE_oc_50kb_gm12878[-1,1],

                      enetcoefs_none_op_50kb_gm12878[-1,1], 
                      enetcoefs_ROS_op_50kb_gm12878[-1,1],
                      enetcoefs_RUS_op_50kb_gm12878[-1,1], 
                      enetcoefs_SMOTE_op_50kb_gm12878[-1,1],

                      enetcoefs_none_dist_50kb_gm12878[-1,1],
                      enetcoefs_ROS_dist_50kb_gm12878[-1,1],
                      enetcoefs_RUS_dist_50kb_gm12878[-1,1],
                      enetcoefs_SMOTE_dist_50kb_gm12878[-1,1])

#####All

```{r}
heatmap.2(enetcoefsmat,
          #cellnote = cormat,  # same data set for cell labels
          #main = "Correlation", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins =c(5,5),     # widens margins around plot
          col=my_palette,       # use on color palette defined earlier
          na.color = "gray",
          #breaks=col_breaks,    # enable color transition at specified limits
          key=FALSE,
          #key.title = "Elastic-Net\nCoefficient",
          #keysize = 1.5,
          dendrogram="row",     # only draw a row dendrogram,
          Rowv = TRUE,
          Colv = FALSE,
          cexRow=0.5,
          cexCol=0.75,
          #labRow = FALSE,
          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
          #lhei=c(.5,6,0),
          sepwidth=c(0.001,0.001),
          sepcolor="black",
          colsep=0:12,
          rowsep=0:nrow(enetcoefsmat)) 
```

#### 100kb

#None
##OC
enetcoefs_none_oc_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OC/ENET/enetModel.rds")
enetcoefs_none_oc_100kb_gm12878 <- coef(enetcoefs_none_oc_100kb_gm12878$finalModel, s=enetcoefs_none_oc_100kb_gm12878$bestTune$lambda)
##OP
enetcoefs_none_op_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OP/ENET/enetModel.rds")
enetcoefs_none_op_100kb_gm12878 <- coef(enetcoefs_none_op_100kb_gm12878$finalModel, s=enetcoefs_none_op_100kb_gm12878$bestTune$lambda)
##Distance
enetcoefs_none_dist_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/ENET/enetModel.rds")
enetcoefs_none_dist_100kb_gm12878 <- coef(enetcoefs_none_dist_100kb_gm12878$finalModel, s=enetcoefs_none_dist_100kb_gm12878$bestTune$lambda)

#RUS
##OC
enetcoefs_RUS_oc_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OC/ENET/enetModel.rds")
enetcoefs_RUS_oc_100kb_gm12878 <- coef(enetcoefs_RUS_oc_100kb_gm12878$finalModel, s=enetcoefs_RUS_oc_100kb_gm12878$bestTune$lambda)
##OP
enetcoefs_RUS_op_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OP/ENET/enetModel.rds")
enetcoefs_RUS_op_100kb_gm12878 <- coef(enetcoefs_RUS_op_100kb_gm12878$finalModel, s=enetcoefs_RUS_op_100kb_gm12878$bestTune$lambda)
##Distance
enetcoefs_RUS_dist_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/ENET/enetModel.rds")
enetcoefs_RUS_dist_100kb_gm12878 <- coef(enetcoefs_RUS_dist_100kb_gm12878$finalModel, s=enetcoefs_RUS_dist_100kb_gm12878$bestTune$lambda)

#ROS
##OC
enetcoefs_ROS_oc_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OC/ENET/enetModel.rds")
enetcoefs_ROS_oc_100kb_gm12878 <- coef(enetcoefs_ROS_oc_100kb_gm12878$finalModel, s=enetcoefs_ROS_oc_100kb_gm12878$bestTune$lambda)
##OP
enetcoefs_ROS_op_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OP/ENET/enetModel.rds")
enetcoefs_ROS_op_100kb_gm12878 <- coef(enetcoefs_ROS_op_100kb_gm12878$finalModel, s=enetcoefs_ROS_op_100kb_gm12878$bestTune$lambda)
##Distance
enetcoefs_ROS_dist_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/ENET/enetModel.rds")
enetcoefs_ROS_dist_100kb_gm12878 <- coef(enetcoefs_ROS_dist_100kb_gm12878$finalModel, s=enetcoefs_ROS_dist_100kb_gm12878$bestTune$lambda)

#SMOTE
##OC
enetcoefs_SMOTE_oc_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OC/ENET/enetModel.rds")
enetcoefs_SMOTE_oc_100kb_gm12878 <- coef(enetcoefs_SMOTE_oc_100kb_gm12878$finalModel, s=enetcoefs_SMOTE_oc_100kb_gm12878$bestTune$lambda)
##OP
enetcoefs_SMOTE_op_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OP/ENET/enetModel.rds")
enetcoefs_SMOTE_op_100kb_gm12878 <- coef(enetcoefs_SMOTE_op_100kb_gm12878$finalModel, s=enetcoefs_SMOTE_op_100kb_gm12878$bestTune$lambda)
##Distance
enetcoefs_SMOTE_dist_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/ENET/enetModel.rds")
enetcoefs_SMOTE_dist_100kb_gm12878 <- coef(enetcoefs_SMOTE_dist_100kb_gm12878$finalModel, s=enetcoefs_SMOTE_dist_100kb_gm12878$bestTune$lambda)

enetcoefsmat <- cbind(enetcoefs_none_oc_100kb_gm12878[-1,1], 
                      enetcoefs_ROS_oc_100kb_gm12878[-1,1],
                      enetcoefs_RUS_oc_100kb_gm12878[-1,1], 
                      enetcoefs_SMOTE_oc_100kb_gm12878[-1,1],

                      enetcoefs_none_op_100kb_gm12878[-1,1], 
                      enetcoefs_ROS_op_100kb_gm12878[-1,1],
                      enetcoefs_RUS_op_100kb_gm12878[-1,1], 
                      enetcoefs_SMOTE_op_100kb_gm12878[-1,1],

                      enetcoefs_none_dist_100kb_gm12878[-1,1],
                      enetcoefs_ROS_dist_100kb_gm12878[-1,1],
                      enetcoefs_RUS_dist_100kb_gm12878[-1,1],
                      enetcoefs_SMOTE_dist_100kb_gm12878[-1,1])

#####All

```{r}
heatmap.2(enetcoefsmat,
          #cellnote = cormat,  # same data set for cell labels
          #main = "Correlation", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins =c(5,5),     # widens margins around plot
          col=my_palette,       # use on color palette defined earlier
          na.color = "gray",
          #breaks=col_breaks,    # enable color transition at specified limits
          key=FALSE,
          #key.title = "Elastic-Net\nCoefficient",
          #keysize = 1.5,
          dendrogram="row",     # only draw a row dendrogram,
          Rowv = TRUE,
          Colv = FALSE,
          cexRow=0.5,
          cexCol=0.75,
          #labRow = FALSE,
          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
          #lhei=c(.5,6,0),
          sepwidth=c(0.001,0.001),
          sepcolor="black",
          colsep=0:12,
          rowsep=0:nrow(enetcoefsmat)) 
```
